The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2011-12-22 smurf_paper.tex
smurf: add some key figures illustrating map degeneracy/constraint concepts

\subsection{Point source}
Reduce a calibrator. Describe the use of a zero mask around the
source. Compare with \citet{wiebe2009} who used the same method to
constrain a maximum-likelihood map with poor cross-linking.

>>>>

In this section three different types of data are reduced. In each
case, the baseline reduction using defaults as described in
Section~\ref{sec:algorithm} are used first. Then, modifications are
described to improve each reduction.

\subsection{Point source}
In this example we produce a map of Uranus, which is a nearly
point-like source for SCUBA-2 that is commonly used as a primary flux
calibrator (observation 26 on 20111017). The first reduction uses the
defaults as described in Section~\ref{sec:algorithm}, but we manually
set the number of iterations to a fixed value of 100 to illustrate how
the solution converges in the absence of any boundary conditions.

Reduce a calibrator. Describe the use of a zero mask around the
source. Compare with \citet{wiebe2009} who used the same method to
constrain a maximum-likelihood map with poor cross-linking.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{pointmaps.pdf}
\caption{Multiple reductions of a 450\,\micron\ daisy scan of Uranus,
  all scaled between -0.002\, pW (white) and +0.002\,pW (black): (a)
  Reduction in which only common-mode subtraction is used to suppress
  low-frequency noise, and the reduction is forced to use 2 iterations
  (after the first iteration an estimate of the source flux is
  removed, and the noise is measured in the residuals to obtain
  appropriate weighting for the second and final iteration) ---
  circular streaks are caused by independent low-frequency noise that
  is not removed by the common-mode; (b) same as (a) but using 50
  iterations, illustrating that there is a degeneracy between
  large-scale structure and the common-mode (the footprint of working
  bolometers is also shown for reference); (c) reduction in which
  high-pass filtering above 0.775\,Hz (corresponding to a spatial
  scale of 200\,arcsec as indicated) is applied after common-mode
  removal, but before the map estimate --- the map-based convergence
  test is activated and the solution halts after 10 iterations, but
  leaving large-scale ringing due to the filter; (d) same as (c), but
  now the region of the map beyond the white dot-dashed circle is
  constrained to a value of zero until all but the final iteration ---
  the map is now extremely flat, there is little attenuation of the
  source flux, and the diffraction pattern is clearly seen.}
\label{fig:pointmaps}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{degeneracy.pdf}
\caption{Demonstration of the degeneracy between large-scale
  structures in the map and common-mode removal, corresponding to
  panels (a) and (b) in Fig.~\ref{fig:pointmaps}. The black and grey
  lines in the top panel show the residual signal for a single
  bolometer after 2 and 50 iterations respectively (they are nearly
  identical). The green and red lines show the \emph{difference}
  between the \model{COM} and \model{AST} (the signal produced by the
  current map estimate for a given bolometer) model components for
  that bolometer between iterations 2 and 50 respectively. This shows
  that a strong signal has grown over time, and it has equal but
  opposite signs in the two model components, so that they cancel one
  another. The bottom panel shows the scan pattern of the telescope
  over the same period; clearly the \model{COM}/\model{AST} model
  degeneracy is correlated with the elevation offset, and referring to
  Fig.~\ref{fig:pointmaps}, panel (b), this clearly corresponds to the
  strong vertical gradient that has appeared}.
\label{fig:degeneracy}
\end{figure}
